% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[5]{min}},
    portion = {\portion{1(hungry)-2(add something)}}
]
{Corn Soup}
    
    \graph
    {% pictures
        small=pic/cornsoup2,     % small picture
        big=pic/cornsoup % big picture
    }
    
    \introduction{%
        This might be the most efficient warm dish I know. The portion is large enough for one hungry person. You can add tortilla chips, pretzels, Karelian pies, etc. to make it a dish for two.
    }
    
    \ingredients{%
        a can of corn \\
        a can of tomato (in pieces)\\        
        \~100g of grated (gouda) cheese\\ 
        salt and (cayenne) pepper
    }
    
    \preparation{%
        \step Put the tomato into a pot and start cooking it. Then add the spices. Add the corn from the can, without the liquid inside.
        \step Let the soup boil a few minutes and then switch of the stove and mix in the cheese. Put the soup into a bowl and let it cool down a little bit.  
}
    \suggestion[]
    {%
        You can try adding other spices, leftover Ajvar, leftover other cheese ... Clean the pot immediately after you're done cooking. If you wait, the cheese cools down and gets harder to remove.
    }
    
    
    \hint{ Since all ingredients don't really need to be cooked, the dish can be done in 2min if you're hungry. (If you leave it longer, the consistency might improve slightly.) \#easy \#for1 \#emergencyoption \#glutenfree \#fast
       
    }
    
\end{recipe}