% Complete recipe example
\begin{recipe}
[% 
    preparationtime = {\unit[60]{min}},
    portion = {\portion{many}}
]
{Mujadara}
    
    \graph
    {% pictures
        small=pic/mujadaraonion,     % small picture
        big=pic/mujadara3 % big picture
    }
    
    \introduction{% 
    This dish was shown to me by Sabaa and Hajo. 
        It is great for gatherings of people. While it takes some time, it does not take much work and you can easily make food for 8 or more people. I will list the ingredients for x cups. x=1 should be enough for 4-5 people.
    }
    
    \ingredients{%
    	x cups dark lentils \\
        2x cups of dark rough bulgur \\
        0.5x cups of olive oil\\
        x tbl of salt \\
        some onions (maybe 2-3x)
    }
    
    \preparation{%
        \step Boil x cups of lentils and 2$\cdot$x + 1 cups of water in a big pot until the lentils are almost done (maybe 20min?). Around 10 min before that, wash the bulgur and soak it.
        \step Add the 2x cups of bulgur and the salt and turn down the heat. If there is less than around 2cm of water on top after adding the water, add some more water. Cook till the water is gone and everythings done.
        \step Meanwhile cut the onions and (deep) fry them in the olive oil. When done add the oil to the ready food in the pot and stir it in. 
}
    \suggestion[]
    {%
        Eat it with a salad. If you have leftovers, they will last a long time. Some of the ingredients you might only get in the turkish market, but they are storable.
    }
    
    
    \hint{ \#prepareinadvance \#vegan \#partyfood \#glutenfree
       
    }
    
\end{recipe}